---
title: "Flytrap Example: Qubit and Gates"
description: |
  This is an example to apply for an internship at Quantum Flytrap
author:
  - name: Claudia Zendejas-Morales
    url: http://claudiazm.xyz
date: "`r Sys.Date()`"
output: distill::distill_article
bibliography: refs.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo=FALSE, message=FALSE, results='asis'}
cat(
  "<link rel='stylesheet' href='https://stackpath.bootstrapcdn.com/bootstrap/4.3.1/css/bootstrap.min.css'>",
  "<script src='https://cdn.jsdelivr.net/npm/vue@2.6.12'></script>",
  "<script src='https://unpkg.com/quantum-tensors@0.4.14/dist/quantum-tensors.min.js'></script>",
  "<script src='https://unpkg.com/bra-ket-vue@0.3.1/dist/bra-ket-vue.min.js'></script>",
  "<script src='https://cdn.jsdelivr.net/npm/sortablejs@1.8.4/Sortable.min.js'></script>",
  "<script src='https://cdnjs.cloudflare.com/ajax/libs/Vue.Draggable/2.20.0/vuedraggable.umd.min.js'></script>",
  "<script src='https://cdn.jsdelivr.net/npm/vue-round-slider@1.0.1/dist/vue-roundslider.min.js'></script>"
)
```


Quantum computing is the use of quantum phenomena such as superposition and entanglement to perform computation.  There are several models of quantum computers, including the quantum circuit model, adiabatic quantum, amog others. Quantum circuits are based on the **qubit**. 

A **qubit** is the equivalent to a *bit* in classical computation. A qubit is a two-state (or two-level) quantum-mechanical system, we write qubits with Dirac notation.

The general quantum state of a qubit can be represented by a linear superposition of its two orthonormal basis states (or basis vectors). These vectors are usually denoted as $|0\rangle$ and $|1\rangle$:

$$|0\rangle = \begin{bmatrix}
1\\
0
\end{bmatrix}
\; \; \; , \; \; \;
|1\rangle = \begin{bmatrix}
0\\
1
\end{bmatrix}$$

Therefore, the quantum state of a qubit $|\psi\rangle$ can be $|\psi\rangle=|0\rangle$ or $|\psi\rangle=|1\rangle$ or $|\psi\rangle=\alpha|0\rangle +\beta|1\rangle$ (a superposition), where $\alpha$ and $\beta$ are complex numbers [@Mermin07].

The **Bloch sphere** is a geometrical representation of the pure state space of a two-level quantum mechanical system (qubit). The north and south poles of the Bloch sphere are typically chosen to correspond to the standard basis vectors $|0\rangle$  and $|1\rangle$, respectively, which in turn might correspond e.g. to the spin-up and spin-down states of an electron.

Therefore, it is possible to define a state using $\theta$ and $\phi$ which correspond to the definition of the Bloch sphere as follows [@Nielsen16]:

$$|\psi\rangle = \cos\left(\tfrac{\theta}{2}\right) \; |0\rangle + e^{i\phi} \; \sin\left(\tfrac{\theta}{2}\right) \; |1\rangle$$

thus,

$$\alpha=\cos\left(\tfrac{\theta}{2}\right) \; \; \; \; \; , \; \; \; \; \; \beta=\left(\cos\phi+i\sin\phi\right)\sin\left(\tfrac{\theta}{2}\right)$$
where,

$$0\leq \theta \leq \pi \; \; \text{and} \; \;  0\leq \phi <2\pi$$

<br>
<br>

To this qubits we can apply **quantum gates**, so we can modify its state. This quantum gates have different effects, let's see some of them when starting with state $|0\rangle$:

<br>

(Click on the quantum gate you want to apply to the qubit $|0\rangle$)


```{r}
HTML("
<div id='gates1'>
  <label>
    <input type='radio' name='gate_applied' v-on:click='show = 1' value='x' checked> 
    X Gate
  </label>
  <label>
    <input type='radio' name='gate_applied' v-on:click='show = 2' value='y'> 
    Y Gate
  </label>
  <label>
    <input type='radio' name='gate_applied' v-on:click='show = 3' value='z'>
    Z Gate
  </label>
  <label>
    <input type='radio' name='gate_applied' v-on:click='show = 4' value='h'>
    H Gate
  </label>
  
  <br><br>

  <div class='gate_title' v-show='show == 1'>
    Apply X Gate:
    <div id='ketlist1'></div>
  </div>
  
  <div class='gate_title' v-show='show == 2'>
    Apply Y Gate:
    <div id='ketlist2'></div>
  </div>
  
  <div class='gate_title' v-show='show == 3'>
    Apply Z Gate:
    <div id='ketlist3'></div>
  </div>
  
  <div class='gate_title' v-show='show == 4'>
    Apply H Gate:
    <div id='ketlist4'></div>
  </div>

</div> <!-- end id='gates1' -->

")
```

<br>
<br>

But we can also start with state $|1\rangle$, to see this, now we use a matrix representation of the quantum gates.

Each gate is a matrix that you multiply by the left of the qubit (remember, a qubit is a vector).

In this representation we can see which is the output (the state after applying a gate) for each possible input ($|0\rangle$ or $|1\rangle$).

<br>

(Place your pointer on the input you want to review and the corresponding output will be the one with a colored circle)

<br>

```{r}
HTML("
  <table align='center' class='matrices'>
    <tr>
      <td align='center'>
        X Gate (Pauli X)
        <div id='gate-x'></div>
      </td>
      <td align='center'>
        Y Gate (Pauli Y)
        <div id='gate-y'></div>
      </td>
    </tr>
    <tr>
      <td align='center'>
        Z Gate (Pauli Z)
        <div id='gate-z'></div>
      </td>
      <td align='center'>
        H Gate (Hadamard)
        <div id='gate-h'></div>
      </td>
    </tr>
  </table>
")
```

<br>
<br>

Of course, you can also apply gates in sequence to modify the state of the qubit as needed depending on your algorithm.

The following example applies the gates $Z$, $H$, $X$ (in that order).

This in Dirac notation looks like:

$$ X \;H \; Z \; |0\rangle $$

Note that the order of application is first the gate closest to state $|0\rangle$ and then the one that follows from right to left.

<div id='ketlist5'></div>

<br>
<br>
<br>


You can test for yourself the effect of the different gates, simply drag the gate you want to apply to the *selected gates* area, to delete a gate from that area, you must drag it to the trash area that appears below when you select a gate.

Observe how the state changes according to the applied gates.

To change the *initial state* use the sliders until you find the desired value for each angle (given in fractions of $\pi$) or you can capture it directly by clicking on the central part of each slider.

<div id='state'>

  <table align="center" style="border:none;">
    <tr>
      <td>
        <!-- Vue Round Slider -->
        <round-slider
          class="theta"
          v-model="thetaVal"
          start-angle="0"
          end-angle="180"
          line-cap="round"
          radius="80"
          width="10"
          animation="false"
          handle-size="22"
          handle-shape="round"
          min="0"
          max="1"
          step="0.01"
          range-color="#ff0055"
          circle-shape="full"
          v-bind:tooltip-format="formatTheta"
          v-bind:value-change="changeAngles">
        </round-slider>
        <!-- === -->
      </td>
      <td>
        <round-slider
          class="phi"
          v-model="phiVal"
          start-angle="0"
          end-angle="360"
          line-cap="round"
          radius="80"
          width="10"
          animation="false"
          handle-size="22"
          handle-shape="round"
          min="0"
          max="2"
          step="0.01"
          range-color="#5c00d3"
          circle-shape="full"
          v-bind:tooltip-format="formatPhi"
          v-bind:value-change="changeAngles">
        </round-slider>
      </td>
    </tr>
  </table>

<p align='center'>
<span style='font-family: Asana Math; font-size:20px;'>
  |&#x03C8;&rangle; = {{state_a}} |0&#x27E9;<!-- ⟩ --> + ( {{state_b}} ) |1&#x27E9;<!-- ⟩ -->
</span>
</p>

</div>
<div id='dnd'></div>
<div id='ketlist6'></div>



```{js, results='asis', echo=FALSE, message=FALSE}

const { Circuit, Gates, Vector, Cx, Dimension } = QuantumTensors;
const { KetListViewer, MatrixViewer } = BraKetVue;


const circuitHistory = [];
Circuit.qubits(1)
  .saveTo(circuitHistory)
  .X(0)
  .saveTo(circuitHistory)

Circuit.qubits(1)
  .Y(0)
  .saveTo(circuitHistory)

Circuit.qubits(1)
  .Z(0)
  .saveTo(circuitHistory)

Circuit.qubits(1)
  .H(0)
  .saveTo(circuitHistory)

const circuitHistoryBig = [];
Circuit.qubits(1)
  .saveTo(circuitHistoryBig)
  .Z(0)
  .saveTo(circuitHistoryBig)
  .H(0)
  .saveTo(circuitHistoryBig)
  .X(0)
  .saveTo(circuitHistoryBig);


function addKetList(name, gate, cirq) {

  new Vue({
    el: '#'+name+cirq,
    template: "<ket-list-viewer :steps='stepsQuantumComputing' :dark-mode='false'/>",
    components: {
      KetListViewer,
    },
    data() {
  	  return {
        stepsQuantumComputing: [
          { value: 'Initial state', vector: circuitHistory[0].vector },
          { value: 'After apply '+gate+' gate', vector: circuitHistory[cirq].vector },
        ],
  	  }
    }
  })
}

function addGate(name, operator) {

  new Vue({
    el: '#'+name,
    template: "<matrix-viewer :operator-raw='operator' :dark-mode='false'/>",
    components: {
      MatrixViewer,
    },
    data() {
  	  return { operator }
    }
  })
}


new Vue({
  el: '#gates1',
  data: {
          show: 1
  }
});


addKetList('ketlist','X',1);
addKetList('ketlist','Y',2);
addKetList('ketlist','Z',3);
addKetList('ketlist','H',4);


addGate('gate-x', Gates.X());
addGate('gate-y', Gates.Y());
addGate('gate-z', Gates.Z());
addGate('gate-h', Gates.H());


new Vue({
  el: '#ketlist5',
  template: "<ket-list-viewer :steps='stepsQuantumComputing' :dark-mode='false'/>",
  components: {
    KetListViewer,
  },
  data() {
	  return {
      stepsQuantumComputing: [
        { value: 'Initial state', vector: circuitHistoryBig[0].vector },
        { value: 'Apply Z gate', vector: circuitHistoryBig[1].vector },
        { value: 'Apply H gate', vector: circuitHistoryBig[2].vector },
        { value: 'Apply X gate', vector: circuitHistoryBig[3].vector },
      ],
	  }
  }
});

updateGates = function() {}

var dnd = new Vue({
  el: '#dnd',
  template: `
  <div>
  
    <div>
      <fieldset class="box-available">
        <legend class="legend-text">Available gates</legend>
        <draggable
          class="row"
          :list="availableGates"
          :group="{ name: '1qGates', pull: 'clone', put: false }"
          :sort="false"
          chosen-class="chosen"
        >
          <div
            v-for="gate in availableGates"
            v-bind:class="gate.class"
            :key="gate.name"
          >
          </div>
        </draggable>
      </fieldset>
    </div>
    
    <br><br>
    
    <table class=table-circuit>
      <tr>
        <td>
          <div>
            <fieldset class="box-selected">
              <legend class="legend-text">Selected gates</legend>
              <draggable
                class="row dragArea"
                :list="selectedGates"
                group="1qGates"
                @change="setGates"
                chosen-class="chosen"
                @choose="showTrashArea"
                @end="hideTrash"
                @update="hideTrash"
              >
                <div
                  v-for="(gate,index) in selectedGates"
                  v-bind:class="gate.class"
                  :key="gate.name"
                  @click="deleteItem(index)"
                >
                </div>
              </draggable>
            </fieldset>
          </div>
        </td>
        <td>
          <span style="font-family: MathJax_Main; font-size:30px;">|&#x03C8;&rangle;</span>
        </td>
      </tr>
      <tr>
        <td>
          <div v-show='showTrash'>
            <fieldset class="box-selected">
              <legend class="legend-text">Trash &#x1F5D1;</legend>
              <draggable
                class="row dragArea"
                :list="deletedGates"
                group="1qGates"
                chosen-class="chosen"
                @add="hideTrash"
              >
              </draggable>
            </fieldset>
          </div>
        </td>
        <td>
        </td>
      </tr>
    </table>
    
  </div>
  `,
  data() {
    return {
      availableGates: [
        { name: "I" , class: "i-class selected" },
        { name: "X" , class: "x-class selected" },
        { name: "Y" , class: "y-class selected" },
        { name: "Z" , class: "z-class selected" },
        { name: "H" , class: "h-class selected" },
        { name: "S" , class: "s-class selected" },
        { name: "T" , class: "t-class selected" }
      ],
      selectedGates: [
        { name: "X" , class: "x-class selected" },
        { name: "H" , class: "h-class selected"}
      ],
      deletedGates: [],
      showTrash: 0,
    };
  },
  methods: {
    deleteItem(index) {
      //this.selectedGates.splice(index, 1);
      //this.setGates();
      this.hideTrash();
    },
    setGates() {
      this.hideTrash();
      updateGates();
    }, 
    showTrashArea() {
      this.showTrash = true;
    },
    hideTrash() {
      this.showTrash = false;
    }
  }
});

var stateSlider = new Vue({
  el: "#state",
  data: {
    thetaVal: 0.5,
    phiVal: 1.0,
    alpha: 0.707,
    beta_r: -0.707,
    beta_i: 0,
  },
  methods: {
    formatTheta() {
      return "<span class='round-slider-font'>&theta; = " + this.thetaVal + " &pi;</span>";
    },
    formatPhi() {
      return "<span class='round-slider-font'>&phi; = " + this.phiVal + " &pi;</span>";
    },
    changeAngles() {
      let cos_theta_2 = Math.cos(this.thetaVal*Math.PI / 2);
      let sin_theta_2 = Math.sin(this.thetaVal*Math.PI / 2);
      let cos_phi = Math.cos(this.phiVal*Math.PI);
      let sin_phi = Math.sin(this.phiVal*Math.PI);
      let b_r = cos_phi * sin_theta_2;
      let b_i = sin_phi * sin_theta_2;
      
      this.alpha = cos_theta_2;
      this.beta_r = b_r ;
      this.beta_i = b_i;
      
      updateGates();
      
    },
  },
  computed: {
  	state_a() {
      let a = Math.round(this.alpha * 1000) / 1000;
    	return a !== 0 ? a : '0';
    },
    state_b() {
      let b_r = Math.round(this.beta_r * 1000) / 1000;
      let b_i = Math.round(this.beta_i * 1000) / 1000;
      if (b_r === 0 && b_i === 0) return '0';
      let sgn = ' + '; 
      if (b_i < 0) { 
        sgn = ' - '; 
        b_i = -b_i;
      }
    	return (b_r !== 0 ? b_r : '') + (b_i !== 0 ? sgn + b_i + ' i' : '');
    },
  },
});


circ = new Circuit(
  Vector.fromArray(
    [Cx(stateSlider.$data.alpha, 0), Cx(stateSlider.$data.beta_r, stateSlider.$data.beta_i)], 
    [Dimension.qubit()]
  ),
  1, 
  [0]
);

var circuitHistoryBig2 = [];
circ = circ.saveTo(circuitHistoryBig2)
              .H(0).saveTo(circuitHistoryBig2)
              .X(0).saveTo(circuitHistoryBig2);

var klv = new Vue({
  el: '#ketlist6',
  template: "<ket-list-viewer :steps='stepsQuantumComputing' :dark-mode='false'/>",
  components: {
    KetListViewer,
  },
  data() {
    return {
      stepsQuantumComputing: [
        { value: 'Initial state', vector: circuitHistoryBig2[0].vector },
        { value: 'Apply H gate', vector: circuitHistoryBig2[1].vector },
        { value: 'Apply X gate', vector: circuitHistoryBig2[2].vector },
      ],
    }
  }
});

updateGates = function() {
  
  var gates = dnd.$data.selectedGates;
  
  var initialState = Vector.fromArray(
    [Cx(stateSlider.$data.alpha, 0), Cx(stateSlider.$data.beta_r, stateSlider.$data.beta_i)], 
    [Dimension.qubit()]
  );
  
  circ = new Circuit(
    initialState,
    1, 
    [0]
  );
  
  circuitHistoryBig2 = [];
  circ = circ.saveTo(circuitHistoryBig2);
  
  var i;
  for (i = gates.length - 1; i >= 0; i--) {
    switch(gates[i].name) {
      case 'X':
        circ.X(0).saveTo(circuitHistoryBig2);
        break;
      case 'Y':
        circ.Y(0).saveTo(circuitHistoryBig2);
        break;
      case 'Z':
        circ.Z(0).saveTo(circuitHistoryBig2);
        break;
      case 'H':
        circ.H(0).saveTo(circuitHistoryBig2);
        break;
       case 'I':
        circ.I(0).saveTo(circuitHistoryBig2);
        break;
      case 'S':
        circ.S(0).saveTo(circuitHistoryBig2);
        break;
      case 'T':
        circ.T(0).saveTo(circuitHistoryBig2);
        break;
      default:
        // default case
    }
  }
  
  
  klv.$data.stepsQuantumComputing.splice(0, klv.$data.stepsQuantumComputing.length);
  klv.$data.stepsQuantumComputing.push({ value: 'Initial state', vector: circuitHistoryBig2[0].vector });
  
  for(i = 1; i < circuitHistoryBig2.length; i++) {
    var namegate = gates[gates.length - i]?.name;
    klv.$data.stepsQuantumComputing.push({ 
      value: 'Apply ' + namegate + ' gate ', 
      vector: circuitHistoryBig2[i].vector });
  }
}


```

```{css, echo=FALSE}
.matrix-viewer {
  margin: auto;
}

.gate_title {
  font-size: 18px;
  font-weight: bold;
  text-align: left;
}

.matrices td {
  border: 10px solid #ffffff;
  background-color: rgba(0,0,0,0.03);
  padding: 3px 3px 3px 3px;
  font-size: 16px;
  font-weight: bold;
}

div .x-class {
  color: #ffffff;
  margin: 3px 3px 3px 3px;
  height: 50px;
  width: 50px;
  cursor: grab;
  background-size: 50px 50px;
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Cpath d='M 342.313 299.152 L 307.503 299.152 L 285.353 266.012 L 263.523 299.152 L 229.003 299.152 L 267.943 245.092 L 230.683 192.262 L 264.743 192.262 L 286.123 223.102 L 307.193 192.262 L 339.873 192.262 L 302.613 243.872 L 342.313 299.152 Z' transform='matrix(0.9286789894104004, 0, 0, 0.9679050445556641, -165.3771514892578, -136.51661682128906)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .y-class {
  color: #ffffff;
  margin: 3px 3px 3px 3px;
  height: 50px;
  width: 50px;
  cursor: grab;
  background-size: 50px 50px;
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(127, 0, 255, 0.6);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(128, 255, 0, 0.6);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Cpath d='M 338.193 192.262 L 297.263 260.822 L 297.263 299.152 L 267.033 299.152 L 267.033 260.362 L 226.263 192.262 L 258.173 192.262 L 283.523 234.712 L 308.873 192.262 L 338.193 192.262 Z' transform='matrix(0.8812999725341797, 0, 0, 0.9684740304946899, -148.7193603515625, -136.82974243164062)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .z-class {
  color: #ffffff;
  margin: 3px 3px 3px 3px;
  height: 50px;
  width: 50px;
  cursor: grab;
  background-size: 50px 50px;
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(0, 255, 255, 0.6);'%3E%3C/rect%3E%3Cpath d='M 273.603 275.502 L 329.033 275.502 L 329.033 299.152 L 234.583 299.152 L 234.583 280.472 L 287.763 217.352 L 235.943 217.352 L 235.943 193.702 L 326.773 193.702 L 326.773 212.382 L 273.603 275.502 Z' transform='matrix(0.9775470495223999, 0, 0, 0.9815950393676758, -174.16375732421875, -140.6441650390625)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .h-class {
  color: #ffffff;
  margin: 3px 3px 3px 3px;
  height: 50px;
  width: 50px;
  cursor: grab;
  background-size: 50px 50px;
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(0, 255, 255, 0.6);'%3E%3C/rect%3E%3Cpath d='M 310.353 193.702 L 340.183 193.702 L 340.183 299.152 L 310.353 299.152 L 310.353 258.032 L 269.683 258.032 L 269.683 299.152 L 239.853 299.152 L 239.853 193.702 L 269.683 193.702 L 269.683 233.322 L 310.353 233.322 L 310.353 193.702 Z' transform='matrix(0.8235750198364258, 0, 0, 0.9815950393676758, -138.8560028076172, -140.6441650390625)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .i-class {
  color: #ffffff;
  margin: 3px 3px 3px 3px;
  height: 50px;
  width: 50px;
  cursor: grab;
  background-size: 50px 50px;
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);'%3E%3C/rect%3E%3Cpath d='M 239.853 299.152 L 239.853 193.702 L 269.683 193.702 L 269.683 299.152 L 239.853 299.152 Z' transform='matrix(0.9788930416107178, 0, 0, 0.9799250364303589, -149.47230529785156, -140.3878631591797)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .s-class {
  color: #ffffff;
  margin: 3px 3px 3px 3px;
  height: 50px;
  width: 50px;
  cursor: grab;
  background-size: 50px 50px;
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(128, 255, 0, 0.6);'%3E%3C/rect%3E%3Cpath d='M 276.913 301.262 C 268.38 301.262 260.096 300.209 252.063 298.102 C 244.03 295.989 237.5 293.175 232.473 289.662 L 242.263 267.672 C 246.983 270.785 252.456 273.295 258.683 275.202 C 264.91 277.109 271.036 278.062 277.063 278.062 C 288.516 278.062 294.243 275.199 294.243 269.472 C 294.243 266.459 292.61 264.225 289.343 262.772 C 286.076 261.319 280.83 259.789 273.603 258.182 C 265.67 256.475 259.04 254.642 253.713 252.682 C 248.393 250.722 243.826 247.582 240.013 243.262 C 236.193 238.949 234.283 233.125 234.283 225.792 C 234.283 219.365 236.04 213.565 239.553 208.392 C 243.073 203.219 248.323 199.125 255.303 196.112 C 262.276 193.099 270.836 191.592 280.983 191.592 C 287.91 191.592 294.74 192.372 301.473 193.932 C 308.2 195.485 314.123 197.769 319.243 200.782 L 310.053 222.932 C 300.013 217.505 290.273 214.792 280.833 214.792 C 274.906 214.792 270.586 215.672 267.873 217.432 C 265.166 219.185 263.813 221.469 263.813 224.282 C 263.813 227.095 265.42 229.205 268.633 230.612 C 271.846 232.019 277.016 233.475 284.143 234.982 C 292.176 236.689 298.83 238.522 304.103 240.482 C 309.376 242.435 313.946 245.549 317.813 249.822 C 321.68 254.089 323.613 259.885 323.613 267.212 C 323.613 273.539 321.856 279.265 318.343 284.392 C 314.83 289.512 309.556 293.602 302.523 296.662 C 295.496 299.729 286.96 301.262 276.913 301.262 Z' transform='matrix(1.0259699821472168, 0, 0, 0.9790090322494507, -185.2677459716797, -139.92605590820312)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .t-class {
  color: #ffffff;
  margin: 3px 3px 3px 3px;
  height: 50px;
  width: 50px;
  cursor: grab;
  background-size: 50px 50px;
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(255, 191, 0, 0.6);'%3E%3C/rect%3E%3Cpath d='M 262.303 299.152 L 262.303 217.352 L 229.913 217.352 L 229.913 193.702 L 324.363 193.702 L 324.363 217.352 L 292.133 217.352 L 292.133 299.152 L 262.303 299.152 Z' transform='matrix(1.036102056503296, 0, 0, 0.9793420433998108, -187.591064453125, -140.02294921875)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .chosen {
  transform: scale(1.1) rotate(-5deg);
  cursor: grabbing;
}

div .box-available {
  border-radius: 0px;
  border: none;
  background-color: rgba(0,0,0,0.05);
  padding: 15px 0px 0px 30px;
  width: 425px;
  height: 120px;
}

.legend-text {
  width: 140px;
  margin: 10px 0px 0px 0px;
  font-size: 120%;
}

div .box-selected {
  border-radius: 0px;
  border: none;
  background-color: rgba(0,0,0,0.05);
  padding: 15px 0px 0px 30px;
  width: auto;
  height: 120px;
}

.table-circuit {
  width: 100%;
  padding: 0px;
  border: 0px;
  margin: 0px;
  border-collapse: collapse;
}

.theta .rs-handle {
  background-color: #ff0055;
  box-shadow: 0px 0px 0px 0px #000;
}

.phi .rs-handle {
  background-color: #5c00d3;
  box-shadow: 0px 0px 0px 0px #000;
}

.round-slider-font {
  font-weight: 500;
  font-family: Asana Math;
}


```

