---
title: "Quantum logic gates for a single qubit, interactively"
description: |
  Drag and drop quantum gates to see how they act on a qubit.
author:
  - name: Claudia Zendejas-Morales
    url: http://claudiazm.xyz
    affiliation: Quantum Flytrap
    affiliation_url: https://quantumflytrap.com
  - name: Piotr Migdał 
    url: https://p.migdal.pl
    affiliation: Quantum Flytrap
    affiliation_url: https://quantumflytrap.com
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    toc: true
    toc_float: true
    self_contained: false
creative_commons: CC BY
bibliography: refs.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo=FALSE, message=FALSE, results='asis'}
cat(
  "<script src='https://cdn.jsdelivr.net/npm/vue@2.6.12'></script>",
  "<script src='https://unpkg.com/quantum-tensors@0.4.14/dist/quantum-tensors.min.js'></script>",
  "<script src='https://unpkg.com/bra-ket-vue@0.3.1/dist/bra-ket-vue.min.js'></script>",
  "<script src='https://cdn.jsdelivr.net/npm/sortablejs@1.8.4/Sortable.min.js'></script>",
  "<script src='https://cdnjs.cloudflare.com/ajax/libs/Vue.Draggable/2.20.0/vuedraggable.umd.min.js'></script>",
  "<script src='https://cdn.jsdelivr.net/npm/vue-round-slider@1.0.1/dist/vue-roundslider.min.js'></script>",
  "<script src='https://cdn.jsdelivr.net/npm/pretty-checkbox-vue@1.1/dist/pretty-checkbox-vue.min.js'></script>",
  "<script src='https://unpkg.com/vue-multiselect@2.1.0'></script>",
  "<link rel='stylesheet' href='https://cdn.jsdelivr.net/npm/pretty-checkbox@3.0/dist/pretty-checkbox.min.css'>",
  "<link rel='stylesheet' href='https://unpkg.com/vue-multiselect@2.1.0/dist/vue-multiselect.min.css'>"
)
```

Quantum computers use quantum physics to perform computation. They use phenomena such as superposition and entanglement that make it possible to use more powerful algorithms than in classical computing [@Nielsen00]. In classical computing, we use the electric signal as the carrier of information. In quantum, we use various implementations, including the polarization of light, the spin of ions, and the states of superconductors.

## Qubit

In classical computing, the basic unit is a bit - 0 or 1. In quantum computing, the basic unit is a qubit. Instead of just two values, we have a vector with two components. In this article, we explore what a single qubit is, and what are the quantum computing operations: 

$$|0\rangle = \begin{bmatrix}
1\\
0
\end{bmatrix}
\hspace{1cm}
|1\rangle = \begin{bmatrix}
0\\
1
\end{bmatrix}$$
In general, a qubit can be any [superposition](https://quantumatlas.umd.edu/entry/superposition) of $|0\rangle$ and $|1\rangle$ - that is

$$|\psi\rangle=\alpha|0\rangle +\beta|1\rangle$$

where $\alpha$ and $\beta$ are [complex numbers](https://www.3blue1brown.com/videos-blog/complex-number-fundamentals-lockdown-math-ep-3), that is numbers $z = x + i y$, were $x$ and $y$ are real numbers and $i$ is an imaginary unit $i^2=-1$.
Here are a few common states:

$$|+\rangle=\frac{|0\rangle+|1\rangle}{\sqrt{2}} \hspace{1cm} |-\rangle=\frac{|0\rangle-|1\rangle}{\sqrt{2}}$$

$$|\!\circlearrowleft \rangle=\frac{|0\rangle+i|1\rangle}{\sqrt{2}} \hspace{1cm} |\!\circlearrowright\rangle=\frac{|0\rangle-i|1\rangle}{\sqrt{2}}$$


If complex numbers are new to you - don’t worry. First, many interesting quantum states, operators, and phenomena can be described without complex numbers. Second, complex numbers are importnt and fun on their own. 


## Operations on a qubit

Instead of [classic logic gates](https://en.wikipedia.org/wiki/Logic_gate), we use [quantum logic gates](link to https://en.wikipedia.org/wiki/Quantum_logic_gate). 
How do they work? Let us pick a state and a quantum gate!

### 1. Pick a state

<div id='states-basis'></div>

<div id='ket-state-basis'></div>


### 2. Pick a gate
<div id='gate_combo'></div>

### 3. Check the result
<div id='ket-res-state-basis-gate'></div>

## Quantum gates

Only identity ($I$) and negation ($X$) are the same in classical and quantum computing. All other gates are specific to quantum computing. For example, Hadamard gate ($H$), while having only real numbers, is enough to show the difference between $|+\rangle$ and $|-\rangle$ states (check it!). Another interesting gate is the square root of negation ($\sqrt{X}$ or $\sqrt{NOT}$). If we apply it twice, we get a negation. Don't worry - later in this post, you will be able to compose gates. 
So, what are the most typical gates?  

<div style='text-align: center;'>
<div align='center' class='matrices'>
  I (Id, 𝟙, identity)
  <div id='gate_I'></div>
</div>
<div align='center' class='matrices'>
  X (Pauli-X, NOT)
  <div id='gate_X'></div>
</div>
<div align='center' class='matrices'>
  Y (Pauli-Y)
  <div id='gate_Y'></div>
</div>
<div align='center' class='matrices'>
  Z (Pauli-Z, 1/2 phase shiift)
  <div id='gate_Z'></div>
</div>
<div align='center' class='matrices'>
  H (Hadamard gate)
  <div id='gate_H'></div>
</div>
<div align='center' class='matrices'>
  S (1/4 phase shift)
  <div id='gate_S'></div>
</div>
<div align='center' class='matrices'>
  T (1/8 phase shift)
  <div id='gate_T'></div>
</div>
<div align='center' class='matrices'>
  &radic;X (square root of NOT)
  <div id='gate_sqrtX'></div>
</div>
</div>

## Quantum circuits

Quantum gates can be composed. In a conventional matrix notation, we read from right to left. That is, $X \;H \; Z \; |0\rangle$ means that we start with state $|0\rangle$, then apply $Z$ gate, then $H$, then $X$. I
It is a historic notation that is going to stay here. While in quantum circuits, we use a typical left to right notation, for the sake of this visualization, we use the matrix notation.

You can interact with various sequences of gates in the section below. Drag the gate you want to apply to the selected gate area. To delete a gate from that area, drag it to the trash area.
You can pick any input state from the gauges. It uses a general parametrization of:

$$|\psi\rangle = \cos\left(\tfrac{\theta}{2}\right) \; |0\rangle + e^{i\phi} \; \sin\left(\tfrac{\theta}{2}\right) \; |1\rangle$$

If you want to avoid complex values, use $\phi=0$ (for positive values) or $\phi=\pi$ (for negative values_)

Observe how the state changes according to the applied gates. In BraKetVue, we use [colors to denote phase of complex numbers](https://en.wikipedia.org/wiki/Domain_coloring)[@DomainColoring20; @Migdal14] and [@Qubism20] for an implementation for [QuTiP](http://qutip.org/).

### Pick any state and compose a circuit

<div id='state'>

  <table align="center" style="border:none;">
    <tr>
      <td>
        <!-- Vue Round Slider -->
        <round-slider
          class="theta"
          v-model="thetaVal"
          start-angle="0"
          end-angle="180"
          line-cap="round"
          radius="80"
          width="10"
          animation="false"
          handle-size="22"
          handle-shape="round"
          min="0"
          max="1"
          step="0.01"
          range-color="#ff0055"
          circle-shape="full"
          v-bind:tooltip-format="formatTheta"
          v-bind:value-change="changeAngles">
        </round-slider>
        <!-- === -->
      </td>
      <td>
        <round-slider
          class="phi"
          v-model="phiVal"
          start-angle="0"
          end-angle="360"
          line-cap="round"
          radius="80"
          width="10"
          animation="false"
          handle-size="22"
          handle-shape="round"
          min="0"
          max="2"
          step="0.01"
          range-color="#5c00d3"
          circle-shape="full"
          v-bind:tooltip-format="formatPhi"
          v-bind:value-change="changeAngles">
        </round-slider>
      </td>
    </tr>
  </table>

<p align='center'>
<span style='font-family: Asana Math; font-size:20px;'>
  |&#x03C8;&rangle; = {{state_a}} |0&#x27E9;<!-- ⟩ --> + ( {{state_b}} ) |1&#x27E9;<!-- ⟩ -->
</span>
</p>

</div>
<div id='dnd'></div>
<div id='ketlist6'></div>

## Remarks

This post is a part of the quantum computing series by [Quantum Flytrap](https://quantumflytrap.com/). We write it using [Distill for R Markdown](https://rstudio.github.io/distill/) - a style based on the [Distill](https://distill.pub/) journal. This article uses [our Quantum Tensors](https://github.com/Quantum-Game/quantum-tensors) library for computing quantum operations, and [BraKetVue](https://github.com/Quantum-Game/bra-ket-vue) for quantum state and operator visualization. These libraries are open source (MIT), as well as this post (CC-BY). The [source to this post is iere](https://github.com/clausia/flytrap-examples). We believe in an open, contributive culture.

Stay tuned for our next posts! The easiest way to do so is to [follow our Twitter account](https://twitter.com/quantumgameio).



```{js, results='asis', echo=FALSE, message=FALSE}

const { Circuit, Gates, Vector, Cx, Dimension, Operator } = QuantumTensors;
const { KetViewer, KetListViewer, MatrixViewer } = BraKetVue;


const circuitHistory = [];
Circuit.qubits(1)
  .saveTo(circuitHistory)
  .X(0)
  .saveTo(circuitHistory)

Circuit.qubits(1)
  .Y(0)
  .saveTo(circuitHistory)

Circuit.qubits(1)
  .Z(0)
  .saveTo(circuitHistory)

Circuit.qubits(1)
  .H(0)
  .saveTo(circuitHistory)

const circuitHistoryBig = [];
Circuit.qubits(1)
  .saveTo(circuitHistoryBig)
  .Z(0)
  .saveTo(circuitHistoryBig)
  .H(0)
  .saveTo(circuitHistoryBig)
  .X(0)
  .saveTo(circuitHistoryBig);


function SqrtX() {
  return Operator.fromSparseCoordNames(
    [
      ['0', '0', Cx(1, 1)],
      ['1', '0', Cx(1, -1)],
      ['0', '1', Cx(1, -1)],
      ['1', '1', Cx(1, 1)],
    ],
    [Dimension.qubit()]
  ).mulConstant(Cx(0.5));
}


function addKetList(name, gate, cirq) {

  new Vue({
    el: '#'+name+cirq,
    template: "<ket-list-viewer :steps='stepsQuantumComputing' :dark-mode='false'/>",
    components: {
      KetListViewer,
    },
    data() {
  	  return {
        stepsQuantumComputing: [
          { value: 'Initial state', vector: circuitHistory[0].vector },
          { value: gate + ' gate', vector: circuitHistory[cirq].vector },
        ],
  	  }
    }
  })
}

function addGate(name, operator) {

  new Vue({
    el: '#'+name,
    template: "<matrix-viewer :operator-raw='operator' :dark-mode='false'/>",
    components: {
      MatrixViewer,
    },
    data() {
  	  return { operator }
    }
  })
}


new Vue({
  el: '#gates1',
  data: {
          show: 1
  }
});


addKetList('ketlist','X',1);
addKetList('ketlist','Y',2);
addKetList('ketlist','Z',3);
addKetList('ketlist','H',4);


addGate('gate_I', Gates.I());
addGate('gate_X', Gates.X());
addGate('gate_Y', Gates.Y());
addGate('gate_Z', Gates.Z());
addGate('gate_H', Gates.H());
addGate('gate_S', Gates.S());
addGate('gate_T', Gates.T());
addGate('gate_sqrtX', SqrtX());


new Vue({
  el: '#ketlist5',
  template: "<ket-list-viewer :steps='stepsQuantumComputing' :dark-mode='false'/>",
  components: {
    KetListViewer,
  },
  data() {
	  return {
      stepsQuantumComputing: [
        { value: 'Initial state', vector: circuitHistoryBig[0].vector },
        { value: 'Z gate', vector: circuitHistoryBig[1].vector },
        { value: 'H gate', vector: circuitHistoryBig[2].vector },
        { value: 'X gate', vector: circuitHistoryBig[3].vector },
      ],
	  }
  }
});

updateGates = function() {}

var dnd = new Vue({
  el: '#dnd',
  template: `
  <div>
  
    <div>
      <fieldset class="box-available">
        <legend class="legend-text">Available gates</legend>
        <draggable
          class="row"
          :list="availableGates"
          :group="{ name: '1qGates', pull: 'clone', put: false }"
          :sort="false"
          chosen-class="chosen"
        >
          <div
            v-for="gate in availableGates"
            v-bind:class="gate.class"
            :key="gate.name"
          >
          </div>
        </draggable>
      </fieldset>
    </div>
    
    <table class=table-circuit>
      <tr>
        <td>
          <div>
            <fieldset class="box-selected">
              <legend class="legend-text">Selected gates</legend>
              <draggable
                class="row dragArea"
                :list="selectedGates"
                group="1qGates"
                @change="setGates"
                chosen-class="chosen"
                @choose="showTrashArea"
                @end="hideTrash"
                @update="hideTrash"
              >
                <div
                  v-for="(gate,index) in selectedGates"
                  v-bind:class="gate.class"
                  :key="gate.name"
                  @click="deleteItem(index)"
                >
                </div>
              </draggable>
            </fieldset>
          </div>
        </td>
        <td width="40px">
          <span style="font-family: MathJax_Main; font-size:30px;">|&#x03C8;&rangle;</span>
        </td>
      </tr>
      <tr>
        <td>
          <div v-show='showTrash'>
            <div class="box-trash">
              <fieldset class="box-selected">
                <legend class="legend-text">Trash &#x1F5D1;</legend>
                <draggable
                  :list="deletedGates"
                  group="1qGates"
                  chosen-class="chosen"
                  @add="hideTrash"
                >
                </draggable>
              </fieldset>
            </div>
          </div>
        </td>
        <td>
        </td>
      </tr>
    </table>
    
  </div>
  `,
  data() {
    return {
      availableGates: [
        { name: "I" , class: "gate-class i-class" },
        { name: "X" , class: "gate-class x-class" },
        { name: "Y" , class: "gate-class y-class" },
        { name: "Z" , class: "gate-class z-class" },
        { name: "H" , class: "gate-class h-class" },
        { name: "S" , class: "gate-class s-class" },
        { name: "T" , class: "gate-class t-class" },
        { name: "sqrtX" , class: "gate-class sqrtx-class" }
      ],
      selectedGates: [
        { name: "X" , class: "gate-class x-class" },
        { name: "H" , class: "gate-class h-class" }
      ],
      deletedGates: [],
      showTrash: 0,
    };
  },
  methods: {
    deleteItem(index) {
      //this.selectedGates.splice(index, 1);
      //this.setGates();
      this.hideTrash();
    },
    setGates() {
      this.hideTrash();
      updateGates();
    }, 
    showTrashArea() {
      this.showTrash = true;
    },
    hideTrash() {
      this.showTrash = false;
    }
  }
});

var stateSlider = new Vue({
  el: "#state",
  data: {
    thetaVal: 0.5,
    phiVal: 1.0,
    alpha: 0.707,
    beta_r: -0.707,
    beta_i: 0,
  },
  methods: {
    formatTheta() {
      return "<span class='round-slider-font'>&theta; = " + this.thetaVal + " &pi;</span>";
    },
    formatPhi() {
      return "<span class='round-slider-font'>&phi; = " + this.phiVal + " &pi;</span>";
    },
    changeAngles() {
      let cos_theta_2 = Math.cos(this.thetaVal*Math.PI / 2);
      let sin_theta_2 = Math.sin(this.thetaVal*Math.PI / 2);
      let cos_phi = Math.cos(this.phiVal*Math.PI);
      let sin_phi = Math.sin(this.phiVal*Math.PI);
      let b_r = cos_phi * sin_theta_2;
      let b_i = sin_phi * sin_theta_2;
      
      this.alpha = cos_theta_2;
      this.beta_r = b_r ;
      this.beta_i = b_i;
      
      updateGates();
      
    },
  },
  computed: {
  	state_a() {
      let a = Math.round(this.alpha * 1000) / 1000;
    	return a !== 0 ? a : '0';
    },
    state_b() {
      let b_r = Math.round(this.beta_r * 1000) / 1000;
      let b_i = Math.round(this.beta_i * 1000) / 1000;
      if (b_r === 0 && b_i === 0) return '0';
      let sgn = ' + '; 
      if (b_i < 0) { 
        sgn = ' - '; 
        b_i = -b_i;
      }
    	return (b_r !== 0 ? b_r : '') + (b_i !== 0 ? sgn + b_i + ' i' : '');
    },
  },
});


circ = new Circuit(
  Vector.fromArray(
    [Cx(stateSlider.$data.alpha, 0), Cx(stateSlider.$data.beta_r, stateSlider.$data.beta_i)], 
    [Dimension.qubit()]
  ),
  1, 
  [0]
);

var circuitHistoryBig2 = [];
circ = circ.saveTo(circuitHistoryBig2)
              .H(0).saveTo(circuitHistoryBig2)
              .X(0).saveTo(circuitHistoryBig2);

var klv = new Vue({
  el: '#ketlist6',
  template: "<ket-list-viewer :steps='stepsQuantumComputing' :dark-mode='false'/>",
  components: {
    KetListViewer,
  },
  data() {
    return {
      stepsQuantumComputing: [
        { value: 'Initial state', vector: circuitHistoryBig2[0].vector },
        { value: 'H gate', vector: circuitHistoryBig2[1].vector },
        { value: 'X gate', vector: circuitHistoryBig2[2].vector },
      ],
    }
  }
});

updateGates = function() {
  
  var gates = dnd.$data.selectedGates;
  
  var initialState = Vector.fromArray(
    [Cx(stateSlider.$data.alpha, 0), Cx(stateSlider.$data.beta_r, stateSlider.$data.beta_i)], 
    [Dimension.qubit()]
  );
  
  circ = new Circuit(
    initialState,
    1, 
    [0]
  );
  
  circuitHistoryBig2 = [];
  circ = circ.saveTo(circuitHistoryBig2);
  
  var i;
  for (i = gates.length - 1; i >= 0; i--) {
    switch(gates[i].name) {
      case 'X':
        circ.X(0).saveTo(circuitHistoryBig2);
        break;
      case 'Y':
        circ.Y(0).saveTo(circuitHistoryBig2);
        break;
      case 'Z':
        circ.Z(0).saveTo(circuitHistoryBig2);
        break;
      case 'H':
        circ.H(0).saveTo(circuitHistoryBig2);
        break;
       case 'I':
        circ.I(0).saveTo(circuitHistoryBig2);
        break;
      case 'S':
        circ.S(0).saveTo(circuitHistoryBig2);
        break;
      case 'T':
        circ.T(0).saveTo(circuitHistoryBig2);
        break;
      case 'sqrtX':
        circ.applyGate(SqrtX(), [0]).saveTo(circuitHistoryBig2);
        break;
      default:
        // default case
    }
  }
  
  
  klv.$data.stepsQuantumComputing.splice(0, klv.$data.stepsQuantumComputing.length);
  klv.$data.stepsQuantumComputing.push({ value: 'Initial state', vector: circuitHistoryBig2[0].vector });
  
  for(i = 1; i < circuitHistoryBig2.length; i++) {
    var namegate = gates[gates.length - i]?.name;
    klv.$data.stepsQuantumComputing.push({ 
      value: namegate + ' gate ', 
      vector: circuitHistoryBig2[i].vector });
  }
}


Vue.use(PrettyCheckbox);

var stateBasis = new Vue({
  el: '#states-basis',
  template: `
    <div style='font-family: MathJax_Main; display: flex'>
  
      <p-radio class="p-switch p-fill state_0" name="switch1" color="success" value="st_0" v-model="picked" @change="changeRadio">|0&rangle;</p-radio>
  
      <p-radio class="p-switch p-fill state_1" name="switch1" color="success" value="st_1" v-model="picked" @change="changeRadio">|1&rangle;</p-radio>
  
      <p-radio class="p-switch p-fill state_p" name="switch1" color="success" value="st_p" v-model="picked" @change="changeRadio">|&plus;&rangle;</p-radio>
  
      <p-radio class="p-switch p-fill state_m" name="switch1" color="success" value="st_m" v-model="picked" @change="changeRadio">|&minus;&rangle;</p-radio>
  
      <p-radio class="p-switch p-fill state_r" name="switch1" color="success" value="st_r" v-model="picked" @change="changeRadio">|⟲&rangle;</p-radio>
  
      <p-radio class="p-switch p-fill state_l" name="switch1" color="success" value="st_l" v-model="picked" @change="changeRadio">|⟳&rangle;</p-radio>
      
    </div>
  `,
  data: {
    picked: "st_0",
  },
  methods: {
    changeRadio: function () {
      updateOneStateAndGate();
    },
  }
});

var comboboxGate = new Vue({
  el: '#gate_combo',
  template: `
    <table align='center' style='border: none; margin: none; padding: none;'>
      <tr>
      <td width='300px' style='min-width: 165px;'>
      <multiselect 
        v-model='value' 
        placeholder='Choose a gate' 
        label='gateDesc' 
        track-by='gateName' 
        :options='options' 
        :option-height='50'
        :show-labels='false'
        @select='selectCombo'
        @input='updateValue'>
      <template 
        slot='singleLabel' 
        slot-scope='props'>
        <div :class='props.option.gateVis'></div>
        {{ props.option.gateDesc }}
      </template>
      <template 
        slot='option'
        slot-scope='props'>
        <div :class='props.option.gateVis'></div>
        {{ props.option.gateDesc }}
      </template>
      </multiselect>
      </td>
      <td width='30px'></td>
      <td>
        <div v-show='showMatrix == "I"'><div id='gate_I_0'></div></div>
        <div v-show='showMatrix == "X"'><div id='gate_X_0'></div></div>
        <div v-show='showMatrix == "Y"'><div id='gate_Y_0'></div></div>
        <div v-show='showMatrix == "Z"'><div id='gate_Z_0'></div></div>
        <div v-show='showMatrix == "H"'><div id='gate_H_0'></div></div>
        <div v-show='showMatrix == "S"'><div id='gate_S_0'></div></div>
        <div v-show='showMatrix == "T"'><div id='gate_T_0'></div></div>
        <div v-show='showMatrix == "sqrtX"'><div id='gate_sqrtX_0'></div></div>
      </td>
      </tr>
    </table>
  `,
  components: {
  	Multiselect: window.VueMultiselect.default
	},
  data: {
    options: [
      { gateDesc: "Identity", gateVis: "gate-class i-class", gateName: "I" },
      { gateDesc: "Pauli X", gateVis: "gate-class x-class", gateName: "X" },
      { gateDesc: "Pauli Y", gateVis: "gate-class y-class", gateName: "Y" },
      { gateDesc: "Pauli Z", gateVis: "gate-class z-class", gateName: "Z" },
      { gateDesc: "Hadamard", gateVis: "gate-class h-class", gateName: "H" },
      { gateDesc: "Phase S", gateVis: "gate-class s-class", gateName: "S" },
      { gateDesc: "Phase T", gateVis: "gate-class t-class", gateName: "T" },
      { gateDesc: "Sqrt X", gateVis: "gate-class sqrtx-class", gateName: "sqrtX" },
    ],
    value: { gateDesc: "Identity", gateVis: "gate-class i-class", gateName: "I" },
    showMatrix: "I",
  },
  methods: {
    selectCombo(selectedOption) {
      this.showMatrix = selectedOption.gateName;
    },
    updateValue() {
      updateOneStateAndGate();
    }
  }
})

addGate('gate_I_0', Gates.I());
addGate('gate_X_0', Gates.X());
addGate('gate_Y_0', Gates.Y());
addGate('gate_Z_0', Gates.Z());
addGate('gate_H_0', Gates.H());
addGate('gate_S_0', Gates.S());
addGate('gate_T_0', Gates.T());
addGate('gate_sqrtX_0', SqrtX());

var circuitHis = [];
Circuit.qubits(1).saveTo(circuitHis);

var oneState = new Vue({
  el: '#ket-state-basis',
  template: "<ket-viewer :vector='vector' :dark-mode='false'/>",
  components: {
    KetViewer,
  },
  data() {
    return { 
      vector: circuitHis[0].vector,
    }
  }
})

var oneStateAndGate = new Vue({
  el: '#ket-res-state-basis-gate',
  template: "<ket-viewer :vector='vector' :dark-mode='false'/>",
  components: {
    KetViewer,
  },
  data() {
    return { 
      vector: circuitHis[0].vector,
    }
  }
})

updateOneStateAndGate = function() {
  
  var alpha;
  var beta;
  
  switch(stateBasis.$data.picked) {
    case 'st_0':
      alpha = Cx(1, 0);
      beta = Cx(0, 0);
      break;
    case 'st_1':
      alpha = Cx(0, 0);
      beta = Cx(1, 0);
      break;
    case 'st_p':
      alpha = Cx(0.707107, 0);
      beta = Cx(0.707107, 0);
      break;
    case 'st_m':
      alpha = Cx(0.707107, 0);
      beta = Cx(-0.707107, 0);
      break;
    case 'st_r':
      alpha = Cx(0.707107, 0);
      beta = Cx(0, 0.707107);
      break;
    case 'st_l':
      alpha = Cx(0.707107, 0);
      beta = Cx(0, -0.707107);
      break;
  }
  
  circuitHis = [];
  circ = new Circuit(
      Vector.fromArray(
        [alpha, beta], 
        [Dimension.qubit()],
      ),
      1, 
      [0]
    ).saveTo(circuitHis);
  
  switch(comboboxGate.$data.value.gateName) {
    case 'X':
      circ.X(0).saveTo(circuitHis);
      break;
    case 'Y':
      circ.Y(0).saveTo(circuitHis);
      break;
    case 'Z':
      circ.Z(0).saveTo(circuitHis);
      break;
    case 'H':
      circ.H(0).saveTo(circuitHis);
      break;
    case 'I':
      circ.I(0).saveTo(circuitHis);
      break;
    case 'S':
      circ.S(0).saveTo(circuitHis);
      break;
    case 'T':
      circ.T(0).saveTo(circuitHis);
      break;
    case 'sqrtX':
      circ.applyGate(SqrtX(), [0]).saveTo(circuitHis);
      break;
    default:
      // default case
  }
  
  oneState.$data.vector = circuitHis[0].vector;
  oneStateAndGate.$data.vector = circuitHis[1].vector;
  
}


```

```{css, echo=FALSE}
.matrix-viewer {
  margin: auto;
}

.matrices {
  display: inline-block;
  text-align: center;
  background-color: rgba(0,0,0,0.03);
  padding: 5px 5px 0px 0px;
  margin: 10px 8px 0px 0px;
  border: 0px 0px 0px 0px;
  font-size: 16px;
  font-weight: bold;
}

div .gate-class {
  display: inline-block;
  margin: 3px 3px 3px 3px;
  height: 50px;
  width: 50px;
  cursor: grab;
  background-size: 50px 50px;
  vertical-align: middle;
}

div .x-class {
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Cpath d='M 342.313 299.152 L 307.503 299.152 L 285.353 266.012 L 263.523 299.152 L 229.003 299.152 L 267.943 245.092 L 230.683 192.262 L 264.743 192.262 L 286.123 223.102 L 307.193 192.262 L 339.873 192.262 L 302.613 243.872 L 342.313 299.152 Z' transform='matrix(0.9286789894104004, 0, 0, 0.9679050445556641, -165.3771514892578, -136.51661682128906)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .y-class {
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(127, 0, 255, 0.6);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(128, 255, 0, 0.6);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Cpath d='M 338.193 192.262 L 297.263 260.822 L 297.263 299.152 L 267.033 299.152 L 267.033 260.362 L 226.263 192.262 L 258.173 192.262 L 283.523 234.712 L 308.873 192.262 L 338.193 192.262 Z' transform='matrix(0.8812999725341797, 0, 0, 0.9684740304946899, -148.7193603515625, -136.82974243164062)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .z-class {
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(0, 255, 255, 0.6);'%3E%3C/rect%3E%3Cpath d='M 273.603 275.502 L 329.033 275.502 L 329.033 299.152 L 234.583 299.152 L 234.583 280.472 L 287.763 217.352 L 235.943 217.352 L 235.943 193.702 L 326.773 193.702 L 326.773 212.382 L 273.603 275.502 Z' transform='matrix(0.9775470495223999, 0, 0, 0.9815950393676758, -174.16375732421875, -140.6441650390625)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .h-class {
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(0, 255, 255, 0.6);'%3E%3C/rect%3E%3Cpath d='M 310.353 193.702 L 340.183 193.702 L 340.183 299.152 L 310.353 299.152 L 310.353 258.032 L 269.683 258.032 L 269.683 299.152 L 239.853 299.152 L 239.853 193.702 L 269.683 193.702 L 269.683 233.322 L 310.353 233.322 L 310.353 193.702 Z' transform='matrix(0.8235750198364258, 0, 0, 0.9815950393676758, -138.8560028076172, -140.6441650390625)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .i-class {
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);'%3E%3C/rect%3E%3Cpath d='M 239.853 299.152 L 239.853 193.702 L 269.683 193.702 L 269.683 299.152 L 239.853 299.152 Z' transform='matrix(0.9788930416107178, 0, 0, 0.9799250364303589, -149.47230529785156, -140.3878631591797)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .s-class {
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(128, 255, 0, 0.6);'%3E%3C/rect%3E%3Cpath d='M 276.913 301.262 C 268.38 301.262 260.096 300.209 252.063 298.102 C 244.03 295.989 237.5 293.175 232.473 289.662 L 242.263 267.672 C 246.983 270.785 252.456 273.295 258.683 275.202 C 264.91 277.109 271.036 278.062 277.063 278.062 C 288.516 278.062 294.243 275.199 294.243 269.472 C 294.243 266.459 292.61 264.225 289.343 262.772 C 286.076 261.319 280.83 259.789 273.603 258.182 C 265.67 256.475 259.04 254.642 253.713 252.682 C 248.393 250.722 243.826 247.582 240.013 243.262 C 236.193 238.949 234.283 233.125 234.283 225.792 C 234.283 219.365 236.04 213.565 239.553 208.392 C 243.073 203.219 248.323 199.125 255.303 196.112 C 262.276 193.099 270.836 191.592 280.983 191.592 C 287.91 191.592 294.74 192.372 301.473 193.932 C 308.2 195.485 314.123 197.769 319.243 200.782 L 310.053 222.932 C 300.013 217.505 290.273 214.792 280.833 214.792 C 274.906 214.792 270.586 215.672 267.873 217.432 C 265.166 219.185 263.813 221.469 263.813 224.282 C 263.813 227.095 265.42 229.205 268.633 230.612 C 271.846 232.019 277.016 233.475 284.143 234.982 C 292.176 236.689 298.83 238.522 304.103 240.482 C 309.376 242.435 313.946 245.549 317.813 249.822 C 321.68 254.089 323.613 259.885 323.613 267.212 C 323.613 273.539 321.856 279.265 318.343 284.392 C 314.83 289.512 309.556 293.602 302.523 296.662 C 295.496 299.729 286.96 301.262 276.913 301.262 Z' transform='matrix(1.0259699821472168, 0, 0, 0.9790090322494507, -185.2677459716797, -139.92605590820312)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .t-class {
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(255, 0, 0, 0.6);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(0, 0, 0, 0.1);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(255, 191, 0, 0.6);'%3E%3C/rect%3E%3Cpath d='M 262.303 299.152 L 262.303 217.352 L 229.913 217.352 L 229.913 193.702 L 324.363 193.702 L 324.363 217.352 L 292.133 217.352 L 292.133 299.152 L 262.303 299.152 Z' transform='matrix(1.036102056503296, 0, 0, 0.9793420433998108, -187.591064453125, -140.02294921875)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3C/svg%3E");
}

div .sqrtx-class {
  background-image: url("data:image/svg+xml,%3Csvg xmlns='http://www.w3.org/2000/svg' viewBox='0 0 200 200' width='200' height='200'%3E%3Crect width='100' height='100' style='fill: rgba(255, 191, 0, 0.6);' data-bx-origin='0.5 0.5'%3E%3C/rect%3E%3Crect x='100' width='100' height='100' style='fill: rgba(255, 0, 191, 0.6);'%3E%3C/rect%3E%3Crect y='100' width='100' height='100' style='fill: rgba(255, 0, 191, 0.6);'%3E%3C/rect%3E%3Crect x='100' y='100' width='100' height='100' style='fill: rgba(255, 191, 0, 0.6);'%3E%3C/rect%3E%3Cg transform='matrix(1, 0, 0, 1, -4.054447, -10.607145)'%3E%3Cpath d='M 340.783 299.152 L 306.443 299.152 L 284.593 266.462 L 263.053 299.152 L 229.013 299.152 L 267.423 245.822 L 230.673 193.702 L 264.263 193.702 L 285.353 224.132 L 306.143 193.702 L 338.373 193.702 L 301.623 244.622 L 340.783 299.152 Z' transform='matrix(0.8669739365577698, 0, 0, 0.9812610149383545, -113.16642761230469, -120.74628448486328)' style='line-height: 222.692px; white-space: pre;'%3E%3C/path%3E%3Cpath d='M 303.759 124.613 L 307.029 124.613 L 295.479 158.303 L 291.909 158.303 L 285.219 140.123 L 280.499 140.123 L 280.499 137.283 L 287.769 137.283 L 293.679 153.843 L 303.759 124.613 Z' transform='matrix(2.5905051231384277, 0, 0, 3.988955020904541, -709.808349609375, -452.89447021484375)' style='white-space: pre;'%3E%3C/path%3E%3Crect x='77.598' y='43.578' width='110' height='7' style=''%3E%3C/rect%3E%3C/g%3E%3C/svg%3E");
}

div .chosen {
  transform: scale(1.1) rotate(-5deg);
  cursor: grabbing;
}

div .box-available {
  border-radius: 0px;
  border: none;
  background-color: rgba(0,0,0,0.05);
  padding: 15px 0px 0px 15px;
  width: 464px;
  height: 100px;
}

.legend-text {
  width: 140px;
  margin: 10px 0px 0px 10px;
  font-size: 120%;
  font-family: -apple-system,BlinkMacSystemFont,"Segoe UI",Roboto,"Helvetica Neue",Arial,"Noto Sans",sans-serif,"Apple Color Emoji","Segoe UI Emoji","Segoe UI Symbol","Noto Color Emoji";
}

div .box-selected {
  border-radius: 0px;
  border: none;
  background-color: rgba(0,0,0,0.05);
  padding: 15px 0px 0px 15px;
  width: auto;
  height: 100px;
}

div .box-trash {
  z-index: 1;
  position: absolute;
  width: 464px;
  background-color: rgb(255,255,255);
}

.table-circuit{
  width: 100%;
  padding: 0px;
  border: 0px;
  margin: 0px;
}

.theta .rs-handle {
  background-color: #ff0055;
  box-shadow: 0px 0px 0px 0px #000;
}

.phi .rs-handle {
  background-color: #5c00d3;
  box-shadow: 0px 0px 0px 0px #000;
}

.round-slider-font {
  font-weight: 500;
  font-family: Asana Math;
}

.pretty.p-switch {
    margin-right: auto;
}

.multiselect__option--highlight {
  background: rgba(0,0,0,0.03);
  color: black;
}

.multiselect__option--selected.multiselect__option--highlight {
  background: rgba(0,0,0,0.1);
  color: black;
}

d-article .ket-list table th {
  border-bottom: none;
}

d-article .ket-list table td {
  border-bottom: 0px;
}

d-article .ket-list table {
  border-collapse: collapse;
  margin-bottom: 0rem;
  border-bottom: none;
}

.quantum-state-viewer.ket .ket-component-bright {
  border-width: 0px;
  border-style: none;
}
```

